---
title: "p8105_hw5_cac2225"
author: "Courtney Chan"
date: "November 7, 2018"
output: github_document
---

#Homework 5

##Problem 0
A github repo and local R project was created, an Rmd file was produced, knitted, and committed to github.

##Problem 1

First loading all necessary packages

```{r loading necessary packages}
library(tidyverse)
library(rvest)
library(dplyr)
library(readr)
library(stringr)

```

Using list.files function to list all of the file names within the data folder and creating a dataframe for the file names. The map function and read_csv function are used to map the contents of each csv file onto the file name dataframe.

```{r naming data folder and vector for filenames}

data_folder = "./data"

file_names = list.files(data_folder)

```

```{r defining reading_csv function}

reading_csv = function(x) {
  
  place_holder = read_csv(file.path(data_folder,x))
}
```

```{r creating df for file_names and mapping csv values}

df_files = data_frame(file_names = file_names) %>% 
mutate(actual_files = map(file_names, reading_csv))

```

The values within the lists are unnested into the dataframe. The dataframe is then tidied by gathering the values into a "week" variable and assigning corresponding observation values. Treatment and id variables are created. Week is mutated into a numeric variable. The treatment values are recoded into "control" and "experimental".

```{r tidying file_name dataframe}

df_files = unnest(df_files) %>% 
  gather(key = week, value = obs_value, week_1:week_8) %>% 
    separate(week, into = c("remove", "week"), sep = "_") %>% 
  rename(treatment_id = file_names) %>%
  mutate(treatment_id = str_replace(treatment_id, ".csv", "")) %>% separate(treatment_id, into = c("treatment", "subj_id"), sep = "_") %>% select(subj_id, treatment, week, obs_value, -starts_with("remove")) %>% 
  mutate(week = as.numeric(week)) %>% 
  mutate(treatment = recode(treatment, "con" = "control", "exp" = "experimental"))

df_files

```

```{r spaghetti plot}

ggplot(df_files, aes(x = week, y = obs_value, color = subj_id)) + 
  facet_grid(.~treatment) + 
  geom_line() + 
  labs(
    title = "Observations over weeks 1-8 for each subject",
    y = "Observation Values"
  ) + 
  theme(legend.background = element_rect(size = .5))

```

A spaghetti plot is created, graphing the changes in observation values for each individual subject. The graphs are separated by treatment type - control and experimental. There is a huge difference between the trends seen in the observation values for the control versus experimental groups. The control groups' values remain fairly low for all 8 weeks, hovering from approximately -1 to 3. Whereas amongst the experimental group there is a large, steady increase of the observational values over the 1-8 weeks, starting at around 0 to3.5 and increasing to around 3 to 6.

##Problem 2

The csv file is imported using the read_csv function and the dataset is cleaned.

```{r}

homicide = read_csv("./data2/homicide-data.csv") %>% 
  janitor::clean_names()

```

Looking at the raw data, the number of observations and number of variables are `r dim(homicide)`. The variable names include `r names(homicide)`. The variables include identifiers describing the victim (id number, first and last name, sex and race), where and when the victim was found (using reported_date, longitude and latitude coordinates, city) and whether the case was closed or still open.

A city_state variable is created using the functions paste and mutate.

```{r creating city_state variable}

homicide = homicide %>% 
  mutate(city_state = paste(city,",",state))

```

```{r summarizing by cities total homicides}

total_num_homicides = homicide %>% 
  group_by(city_state) %>% 
  summarize(total_num_hom = n())

```

```{r summarizing by cities number of unsolved homicides}

unsolved_homicides = homicide %>% 
  filter(disposition == "Closed without arrest" | disposition == "Open/No arrest") %>% 
  group_by(city_state) %>% 
  summarize(num_unsolved_hom = n())

```

The number of total homicides are added up per city_state. The number of unsolved homicides based on disposition status is added up per city_state.

```{r proportion of unsolve homicides in Baltimore, MD}

df_combined = merge(total_num_homicides, unsolved_homicides, by.x = "city_state", by.y = "city_state")

df_combined_BMD = df_combined %>% 
  filter(city_state == "Baltimore , MD")

prop_BMD = prop.test(df_combined_BMD$num_unsolved_hom, df_combined_BMD$total_num_hom) %>% broom::tidy()

ouput_bmd = prop_BMD[c(1,5,6)]

```
